An Open Repository of Real-Time COVID-19 Indicators

### 2021-06-17 indicators/paper/paper.tex
Attemt to draft a complete abstract

% Please add a significance statement to explain the relevance of your work
\significancestatement{To study the COVID-19 pandemic, its effects on society,
  and measures for reducing its spread, researchers need detailed data on the
  course of the pandemic. Standard public health data streams suffer
  inconsistent reporting and frequent, unexpected revisions. They also miss
  other aspects of a population's behavior, worthy of consideration. We
  present an open database of COVID signals in the United States, measured at
  the county level and updated daily. These include traditionally reported COVID
  cases and deaths, and many others: signals based on measures of mobility,
  social distancing, internet search trends, self-reported symptoms, and
  patterns COVID-related activity in de-identified medical insurance claims. The
  database provides all signals in a common, easy-to-use format, empowering both
  public health research and operational decision-making.
}

@@

\begin{abstract}
  Please provide an abstract of no more than 250 words in a single paragraph.
  Abstracts should explain to the general reader the major contributions of the
  article. References in the abstract must be cited in full within the abstract
  itself and cited in the text.
\end{abstract}

>>>>

% Please add a significance statement to explain the relevance of your work
\significancestatement{To study the COVID-19 pandemic, its effects on society,
  and measures for reducing its spread, researchers need detailed data on the
  course of the pandemic. Standard public health data streams suffer
  inconsistent reporting and frequent, unexpected revisions. They also miss
  other aspects of a population's behavior that are worthy of consideration. We
  present an open database of COVID signals in the United States, measured at
  the county level and updated daily. These include traditionally reported COVID
  cases and deaths, and many others: signals based on measures of mobility,
  social distancing, Internet search trends, self-reported symptoms, and
  patterns COVID-related activity in de-identified medical insurance claims. The
  database provides all signals in a common, easy-to-use format, empowering both
  public health research and operational decision-making.
}

@@

\begin{abstract} % 250 words max, one paragraph
  The COVID-19 pandemic in the United States presented enormous data challenges.
  Policymakers, epidemiological modelers, and health researchers all require
  up-to-date data on the pandemic and relevant public behavior, ideally at fine
  spatial and temporal resolution. We present the COVIDcast API, which provides
  an open database of both traditional public health surveillance signals (such
  as cases, deaths, and hospitalizations) and unique indicators of COVID-19
  activity, such as signals extracted from de-identified medical claims data,
  massive online surveys, cell phone mobility data, and Internet search trends.
  These signals are available at a fine geographic resolution (mostly at the
  county level) and are updated daily. Unlike most public health databases, the
  COVIDcast API also tracks all revisions to historical data, allowing modelers
  to account for the frequent revisions and backfill that are common for many
  public health data sources. All data is available in a common format through
  an API and software packages. We describe the data and formats, and present
  examples demonstrating that the non-traditional data sources present in the
  COVIDcast API present information relevant to tracking COVID activity,
  augmenting standard public health reporting and enabling research.
\end{abstract}
